\chapter{Preface}
This is a re-working, in my own words, of David Pingree's translation of Dorotheus of Sidon's \textsl{Carmen Astrolgicum} primarily to make it easier to reference and study. If you are looking for the original text of the translation, there are a number of them online, most notably a copy of Pingree's original book on \href{https://archive.org/details/PingreeDS1976}{Archive.org} or Deborah Houlding's copies of Pingree's translation along with her notes on the text: \href{https://www.skyscript.co.uk/dorotheus1.pdf}{Book I}, \href{https://www.skyscript.co.uk/dorotheus2.pdf}{Book II}, \href{https://www.skyscript.co.uk/dorotheus3.pdf}{Book III}, \href{https://www.skyscript.co.uk/dorotheus3notes.pdf}{Book III Notes}.

The public domain \href{https://www.ctan.org/pkg/starfont}{StarFont Sans} astrological fonts used in this document were created by Anthony I.P. Owen and made available as a Latex package by Matthew Skala. 

This document was built from Latex files created with the \href{https://www.tug.org/texworks/}{TexWorks} editor.

\section{Other works consulted}
\begin{description}
\item[CA]
	\textsl{Carmen Astrologicum: Dorotheus of Sidon} trans. David Pingree, Astrology Classics, 2005

\item[CAD]
	\textsl{Carmen Astrologicum: Dorotheus of Sidon: The 'Umar Al-Tabari Translation} trans. Benjamin N. Dykes. 2019.

\item[CAP]
	\textsl{Carmen Astrologicum: Dorotheus of Sidon} trans. David Pingree, Ascella, 1993.
	
\item[DH]
	\textsl{Notes on Doroheus III:the haylāj, kadhkhudāh, and terms of life} by Deborah Houlding, \href{https://www.skyscript.co.uk/dorotheus3notes.pdf}{URL}, as at August 03, 2020
	
\item[HHA]
	\textsl{A History of Horoscopic Astrology}, James Herschel Holden, AFA, 2nd. ed. 2006
\end{description}

\section{Useful Resources}

\noindent\href{https://www.jcremers.com/}{PlanetDance Astrology Software}

	A free astrology software application created by J.C. Remers. Includes a number Hellenistic Greek techniques under Horoscope->Classical.

\noindent\href{http://www.projecthindsight.com/images/TablesPDFs/Tb2-AscT-sysAB.pdf}{Table of Hellenistic Ascenional Times}
	
	\noindent\href{https://horoscopes.astro-seek.com/calculate-ascensional-rising-times/?latitude=&narozeni_lat_custom_stupne=0&narozeni_lat_custom_minuty=0&narozeni_lat_custom_smer=0&narozeni_rok=2022&aya=&oa=&decimal=0}{Ascensional Rising Times \& Oblique Ascension Tables}
	
	One of the many astrology tools on the \textsl{AstroSeek} web site.
	
	\noindent\href{https://horoscopes.astro-seek.com/traditional-astrology}{Traditional Chart Calculator}
	
	AstroSeek chart calculator that produces a clean graphic with planet dignities, 7 Hermetic Lots, dodecatemoria, as well the ability to calculate circumambulations, profections, antiscia, and more.
	
\newpage
