\section{Which of two adversaries facing a judge will prevail?}
Look at the ascendant at the time you are asked as it indicates \textsl{``the matter of incitements and commencements of quarrels''}. In a fixed sign it indicates the \textsl{``seeker of the right will be keen in his request and will not turn away from his argument''}.

If the ascendant's sign is double-bodied, it indicates the ``seeker of the right'' will be of two minds and regret his quarrel. If the ascendant's sign is tropical, \textsl{``then it indicates that this quarrel will not be finished and will have no end.''}

If \Mars\, is with or aspects the ascendant it indicates grief and shame will reach the one who started the quarrel.

If \Mercury\, is in the ascendant with benefics or aspects the ascendant, it indicates the ``seeker of the right'' will attain dirhams (UAE currency) and goods from his adversary and will turn from quarrelling with the defendant.

If \Saturn\, is with or aspects the ascendant \textsl{``then misery will happen to the seeker because of the quarrel.''}

If, at the time the question is asked, the malefics aspect the midheaven then the quarrel will not be ended but be put before a second judge and the judges will come to shame and a base reputation and disgrace and the two adversaries will settle the matter between themselves by  coming to an agreement on amends. If \Saturn\, is in the midheaven, the judges, by the injustice of their judgment, will suffer shame, misery, and loathing. If benefics are in the midheaven the judge is just and will not be unjust in his decision.

See the condition of the defendant in the seventh sign. If the malefics are in or aspecting the sign then misery and misfortune and pain will occur to him. If \Mercury\, is with the malefics in this sign or aspects it, it indicates that the defendant will be deprived of his wish by injustice and false testimony.

For the outcome of the quarrel, look to the fourth house. If the ruler of the ascendant, midheaven or seventh house is eastern and in the same sign as the lord of the fourth then victory is indicated for the one more suited to the angle whose ruler is eastern with the lord of the fourth unless that planet is under the Sun's rays which indicates loss and defeat.

If the lord of the ascendant and the lord of the seventh are both eastern and with the lord of the fourth it indicates the two adversaries will become reconciled and friendship will thrive between the two. If both of them are under the Sun's rays with the lord of the fourth, then the quarrel will be long and linger and will have no end.

\textsl{``The benefics indicate what there is of success and victory and a just judgment.''}

If the malefics are direct, western, in an angle but not in their own dignities the owner of the angle will be defeated but if they are in their dignities the owner of the angle \textsl{``will attain success by means of the injustice of the judge or because of bribes or forcibly or [by means of] favoritism.''}

\textsl{``The second sign from the seventh indicates the defendent's assistance.''}

If the lord of the ascendant and the lord of the midheaven are together in the same sign or in the ascendant or if the lord of the midheaven aspects the ascendant or the lord of the ascendant \textsl{``then it indicates that the judge will help the seeker and will be on his side.''} but if the lord of the midheaven and the lord of the descendent are in the described condition, \textsl{``then the judge's sympathy and assistance will be for the defendent, and he will attain success because of this.''}

In relation to all these subjects (seeker, defendent, judges, quarrelling, and who will win) also pay attention to the \Moon, if it is in an angular or succedent house and is  injured or it conjoins with malefics before entering under the Sun's rays then the person connected with the house it occupies will lose and suffer misfortune or regret because of the quarrel.

If two adversaries quarrel about a debt or money and bring it before the judges when the \Moon\, is waxing, then the \Moon\, is an indicator for the one who lent the money and the \Sun\, is the indicator for the debtor. If the \Moon\, is waning, then the indicators are reversed.  The indicator who is has the closest aspect to the Ascendant is the more powerful and to that one belongs success.

In every case, always look at Fortune; if she is in the ascendent or second sign from the ascendent, then success will belong to the seeker. If she is in the 7th or 8th sign from the ascendent then success belongs to the defendent. If the lord of the lot is in the 4th and aspects both the 1st and 7th, the two adversaries will be reconciled of their own accord but if it is in the 10th and aspects the 1st and 7th then the reconciliation between the two will be because of the judge.

If the lord of the ascendent and the lord of the 7th are in the same sign in their figures decans, it indicates that the two will be enemies. If the two are in a sign ruled by 
\begin{itemize}[topsep=0em,itemsep=0em]
\item [\Mercury] then their quarrel will be stirred up because of children or one who is in the position of a child. 
\item[\Venus] the quarrel will be because of women or sisters or one in who's position is like that
\item[\Mars] the quarrel will be because of sisters or the children of sisters or brothers
\item[\Saturn\, or \Sun] the quarrel will because of fathers or grandfathers or one who is in a like position
\item[\Moon] the quarrel will be because of mothers or one in a like position
\item[\Jupiter] it indicates the quarrel will be because of older brothers or brothers and friends
\end{itemize}










