\section{On the recovery of goods stolen, lost, or mislaid}
If asked about whether stolen, lost, or mislaid goods will be recovered look at the two lights and if, at the time of asking, each light is in trine to its dispositor, the goods will be recovered quickly and without pain.

If the \Sun\, and \Moon\, are square, the lost goods will be found with trouble and after a long time; the thieves will have moved the goods from their original hiding place to another.

If the \Sun\, and \Moon\, are opposed, the goods will be found, with trouble, after a time.

If the \Moon\, is found in a house along with the planet owning the house, then the goods will be found; especially if the \Sun\, also aspects the place.

If the dodecatemorion (12th part) of the \Moon\, is in one of the ascendant, midheaven, the same sign as the \Sun, or the sign holding the lord of the \Moon, or a sign with an eastern\footnote{Probably means a planet that is eastern with respect to the \Sun.} planet, then the goods will be found.

If the \Sun\, is with, or aspects, the Lot of Fortune, it indicates the goods will soon be recovered.

If the \Moon\, is with or aspects Fortune without it being with or aspected by the \Sun\, it indicates the goods will be recovered but with slowness and trouble.

The \Moon\, or both lights are in the ascendant it indicates a quick recovery of what was lost or stolen.

If the two lights are in the sign opposite the ascending sign will only recover the goods with slowness and trouble or a quarrel and insult and fighting.

If the \Sun\, is alone in the ascendant and the ascendant is not in \Aquarius, \Gemini, or \Libra\, (all signs which oppose the signs where the \Sun\, is in his triplicity) he will recover what was lost or stolen. \textsl{If [the \Sun] is in one of those three signs it will be bad and it will not be suitable for him to possess it.}

If the person's nativity is known and, at the time the goods were lost or stolen, the \Sun\, was in the ascendant while the \Moon\, was in a sign that holds a benefic in the nativity, the indication is that the person will recover what was lost.

\subsection{Unlikely to be found}

If the \Moon\, is in the end degrees of the sign opposite the ascendant sign or the second sign from it, the indication is the goods will not be found, but, if the \Sun\, is trine the \Moon, then the goods will likely be found as the \Sun\, illuminates everything dark and overcomes it, if God wishes.

If the \Moon\, is in the ``burned way'' then it indicates the person will either not recover the goods or they will recover them only after trouble and delay.

If both lights are under the Earth it indicates the goods will disappear and not be recovered.

If neither light is with or aspecting Fortune it indicates the owner might as well not bother looking for the goods as it would bring only toil and not accomplish anything.

If the \Moon\, is under the \Sun's rays and waxing it indicates the person will not perfectly recover their goods \textsl{``because this is an unavoidable judgment''}.

\subsection{Using the angles for various significators}
Some ancients used the ascendant (1st) as the significator of the stolen or lost goods, the midheaven (10th) for the good's owner; the sign opposite the ascendant (7th) for the thief, and IC (4th) for the thieves den and hiding place.

If benefics are in the ascendant the goods will be returned to the owner.

If a planet in the midheaven is in his own dignities then the owner of the goods is sincere and will seek his good in the proper manner; if the planet is not in its own dignities it has no power in the midheaven and the seeker is not truthful.

If the sign on the IC is mutable the stolen property belongs to two men; if in a tropical sign, it belongs to one man; if in a feminine sign the goods belong to women.

If the sign on the IC is moist then what was stolen or lost is near a sea or spring or stream or a valley or a river or a canal or a place where there is water. If in a quadruped sign the stolen goods are in \textsl{``the dung of sheep or the shelter of animals or in the place where animals are tied up or the habitations of animals.''}.
	
If the IC is in a human sign and \Jupiter\, and \Venus\, aspect it, then the goods are in a good and clean place. If, instead, \Mars\, aspects, they are in a place where fire is found, or a blacksmith's forge or something similar. If \Saturn\, aspects, the thieves handed the goods over to slaves who placed them in a dark house or a filthy place open to the wind or a lofty, moist, dark, and dirty place.

If \Jupiter\, occupies the IC while \Saturn\, aspects the place then the goods were handed over to a person of noble lineage. If \Mars, rather than \Jupiter, is in the IC then the person receiving the stolen goods will have the loathsome character of a slave or one free for the day. 

If, instead, \Venus\, is in the first 20 degrees of the IC then the thieves will have stolen the goods from propertied women of noble lineage. If it is in the last 10 degrees of the sign of the IC then slave girls or those who do the work of slave girls will take the stolen items from the thieves.

If, instead, \Mercury\, is in the first 10 degrees of the sign on the IC, then a man of noble lineage and wisdom and of good reputation will take what was stolen from the thieves. If in the middle 10 degrees, a poor man will take the goods from the thieves and will be \textsl{``master of wealth and good fortune for the day''}. If in the last 10 degrees, the man who takes the goods from the thieves is a slave or a man who does the work of slaves.

\subsection{Indications from the Lights}
If the \Sun\, aspects Fortune then the owner will soon recover his goods. If, instead, the \Moon\, aspects Fortune without the aspect of the \Sun, the goods will be recovered after a delay. If neither light aspects Fortune or the Ascendant the goods will only be recovered after trouble and pain.

If the \Moon\, is square, trine, or in the sign opposite the ascendant then the lost or stolen goods will be recovered. 

If the \Sun\,  was trine, square, or in opposition to the \Moon\, while he was in the ascendant or midheaven or with Fortune or aspecting the angles then the goods will be properly recovered. 

If the \Moon\, is the last degrees of a sign (the 3rd decan), then the stolen goods will be moved from place to place.

\subsection{Moon's term gives condition of the goods}
The \Moon\, is indicator of the condition of the goods, lost or stolen. If the \Moon\, is in the term of:
\begin{itemize}[topsep=0em,itemsep=0em]
\item[\Saturn] while \Saturn\, is in the midheaven or in its exaltation, then the goods stolen are costly and necessary in farming or building or acquiring property. If \Saturn\, is under the earth (in the 4th?) then the goods are filthy, shabby, and worn. If \Saturn\, is in a cadent place or in \Aries, his Fall, then the goods are vile, filthy, and broken and if he aspects the \Moon\, then it indicates there is a coarseness or roughness in what was stolen or lost.
\item[\Jupiter] the goods are costly, gold or silver or silk brocades or lustrous in some manner; all things which only the wealthy can afford
\item[\Mars] the goods are something that was worked in fire or a blacksmith's forge or kiln or something similar. If \Mars\, and \Mercury\, both aspect the \Moon\, then the goods were worked by a master craftsman. If \Mars\, does not aspect the \Moon\, but \Venus\, or \Mercury\, do, then the goods are dyed or ring-stones or amulets or covered with all sorts of jewels.
\item[\Venus] what was stolen or lost is gold or silver or a jewel or a costly stone or garments made of beautiful cloth or something dyed in fiery colours, or perfumed or a necklace or trinkets used by women, or something moist, with an agreeable odour, which has a lustre and which women crave or are astonished at. If the \Moon\, is square \Venus\, or with \Venus\, in a feminine sign, the goods were stolen from a woman. If \Mars\, aspects \Venus\, then the object is a jewel that has no lustre but was worked with delicate craftsmanship.
\item[\Mercury] then what was lost or stolen was a book or ledger full of layers [pages?] or a ledger which contains a book of the learned or what is necessary for women or men, or what is necessary on journeys like denarii and dirhams and what has been minted into coinage.
\end{itemize}

\subsection{What the Moon's sign indicates}
The power of the signs is to be mixed with the terms. 
\begin{itemize}[topsep=0em,itemsep=0em]
\item[\Aries] garments, clothes, or trinkets worn on the head or face were lost or stolen
\item[\Taurus] what was stolen gold or silver or trinkets used for adornment\footnote{Dykes says for things that adorn the neck.} or they are something useful for vows\footnote{Dykes has `offerings'.} and for mosques and deities
\item[\Gemini] dirhams or denarii (coins) was stolen or something useful in trades or a ledger which is a book or an idol useful for the deities
\item[\Cancer] a costly gem or something moist was stolen
\item[\Leo] something gold or silver or made from brass was stolen
\item[\Virgo] a woman's trinkets or denarri (coins) was stolen
\item[\Libra] what was stolen has a mixture of things in it or is something useful for the body, or bought for its weight or trinkets useful for eternity
\item[\Scorpio] something of gold, silver, or brass was stolen or else a stone with no lustre
\item[\Sagittarius] something variegated with all sorts of jewels that is craved and competed for and is precious to its people
\item[\Capricorn] like the things stolen or lost when the \Moon\, is in \Cancer; a costly gem or something moist or similar to these things
\item[\Aquarius] like the things stolen or lost when the \Moon\, is in \Leo; something made of gold or silver or brass or similar to these
\item[\Pisces] like the things stolen when the \Moon\, is in Sagittarius; jewelled and precious to its people
\end{itemize}

\subsection{More on the Moon}
If the \Moon\, is waxing and moving faster than average then the goods stolen were new, if the \Moon\, is waning and moving slower than average the goods stolen were shabby or worn.

If the Ascendant or a conjunction of the \Moon\, occurs in a mutable sign then the goods are folded or is made of joined parts.

The quantity of goods stolen is shown by the number of signs\footnote{Pingree says to count the degree between the beginning of the \Moon's sign and \Mercury, I've followed Dykes interpretation as it makes more sense given the context.} between the \Moon's sign and  \Mercury's.  If the number is even (feminine) then the goods are tied together or there was more than one good stolen. If odd (masculine)then only one thing was stolen.

\subsection{Identifying the thief}
If the two lights aspect the Ascendant then the theft was an inside job.  If only one light aspects the ascendant and the other is not in the ascendant and does not aspect it then the thief was someone  who frequents the place and is known to the owner. If neither light aspects the ascendant the thief is an outsider, unknown to the good's owner, and someone who has not frequented the place.

For a description of the thief examine the planets in the 7th, if it's empty, look for planets in the 9th or 12th; if both are empty see which planet the \Moon\, is with or, if alone, which planet she is separating from and applying as these will indicate the key characteristics and colouring of the thief.

If the indicator of the thief is:
\begin{itemize}[topsep=0em,itemsep=0em]
\item[\Jupiter] they will be white, fat, great in his eyes, the white's of the eyes will be smaller than expected, their beards will be round and curly and by nature they will be gentle and good
\item[\Saturn] the thief has a  repulsive face, black in colour; his gaze is toward the ground, he is a broken man with small eyes; slim, twisted in his gaze; with a pallid look; hairy limbs, eyebrows grown together; he is a liar, sickly, his gentleness and nature is in accordance with secrets and tricks; he is profound, contemplative, and has ideas
\item[\Mars] he will be reddish in colour with lank, reddish hair; he is sharp in his vision, fat-cheeked, gay, a master of joking, capricious, turning himself from one condition to another, sharp in his glance; he rushes to injure men and to obliterate their things
\item[\Venus]  the thief is handsome, with an abundant hair on his head, fate, handsome eyes with the black of his eyes greater than the whites; white in his extremities and his colour but mixed with redness; he is fat, good in his gentleness and manner, he submits courteously to a command
\item[\Mercury] the thief is slim, emaciated, has good bones, powerful, bald, with a handsome beard, pale, not straight in his thinking
\item[\Sun] when the \Sun\, is on his own, not strongly aspected, and is the indicator of the thief, he will be fat, with red and yellow eyes
\item[\Moon] if the \Moon\, is not closely connected to another planet and she is the indicator of the thief then they are comely in appearance, white, and fat-cheeked
\end{itemize}

Mix the nature of the sign occupied by the planet that indicates the thief with the planet's nature to get a more complete picture of the thief's characteristics and manner:

\begin{itemize}[topsep=0em,itemsep=0em]
\item[\Aries] his limbs are full of hair, he is handsome in stature, his gaze is toward the ground, he is bald, joyful, gay in his face, humorous, impudent in his speech
\item[\Taurus] he is sharp-nosed, with a broad, protruding forehead,  elevated hair\footnote{Dykes has `trussed-up hair'}; his character is not known as it can vary widely, he finds power in what is hidden [secrets], in deception, and in trickery; he has broad nostrils, a fat, burly neck, black eyes; his eyebrows are smaller than the width of his eyes, and he is on the short side
\item[\Gemini] he has a powerful stance, wide shoulders; his gentleness and character are good; some of them write, some who were trusted, and had a position among men, who were pleasant in their view
\item[\Cancer] large shoulder-blades, solid bones; no hair, stingy, glum-faced, black in colour, gag-toothed, powerful stance, lower limbs more powerful than upper limbs
\item[\Leo] the thief is blue, red-haired, reddish in colour, lank-haired, comely in appearance, superior in his higher joints which are more ample than his lower, slender legs, irascible, coarse, sharp-sighted as a lion; some are epileptic and known for it
\item[\Virgo] has a straight posture, handsome body, a powerful stance and limbs, not excessively fat or slim, humorous, good in his gentleness, trustworthy, sincere, one of those who is educated in writing and what it is useful for, coveted for this, profitable in his uprightness and his friendliness in an affair
\item[\Libra] handsome face and colouring, white, equal in his limbs; one of them does not differ from the other; he was educated in beating on strings and singing and the rules of tune and of poetry; a handsome face, goo i his manner in calculating his livelihood, learned in words; he tends toward what is in the power of \Venus\, and lust for women, is greedy and stimulated toward it
\item[\Scorpio] thick hair on his hands, elevated hair; no black in the pupil of his eye; bluish-black, powerful eyes, fat cheeks, small, narrow, protruding forehead; long-legged, large feet, wide shoulders; prone to embezzlement; hastens to his affairs with little diffidence or reflection; a disgraceful reputation, unpleasant
\item[\Sagittarius] long-legged, wide-thighed; the back of him is more attractive than the front; a lank long but small beard, red in his colour, clever, agile, delicate, a run-away slave, a marksman, works with his hands; he is a profiteer, a wastrel, a generous man; some have a craving for animals, some are bald
\item[\Capricorn] thin-legged, miserable in his two legs, slim, a male; his face resembles that of a goat's in the dark; lank beard, sharp-eyed; his glance is toward the ground, his opinion does not change from one situation to another; trivial in thought and consideration
\item[\Aquarius] neither tall nor slight put with a powerful stance, eager for ornamentation, eager for gathering properties, handsome beard, pleasing in his diet, good in his gentleness in his meals and in cleaning himself, abounding in expenses; one of his legs is longer or larger than the other
\item[\Pisces] wide shoulders, abundant hair on his head, small-headed, small-faced, narrow in his two sides; the blacks of his eyes are greater than the whites; bending down, he loves himself, is twisted in his sight
\end{itemize}

If a benefic aspects the planet indicating the thief he is of a noble lineage. If the malefics aspect the indicator, then he is a slave or one who does service.

If \Venus\, is the indicator, the thief is a woman or a lady who steals for women.

If \Mercury\, is the indicator, the thief is a boy or a youth, or young man.

If \Mars\, is the indicator, he is a young man.

If \Jupiter\, is the indicator, the thief is middle-aged.

If \Saturn\, is the indicator, the thief is old.

If the indicator is eastern, the thief is young; if western, he is not a youth but older.

If the indicator is at his first station, the thief is advanced in years, closer to old age than to youth. At second stage they are even closer to old age. If the indicator is coming out from under the Sun's rays and is eastern, it indicates youth; if coming out and western, it indicates they are an elder\footnote{This probably applies to the inner planets who an emerge from under the Sun's rays either ahead (east) of the Sun or behind (west) of the Sun.}

If \Saturn\, is coming out from under the Sun's rays or becomes eastern then mix in his old age and whenever \Saturn\, is eastern the thief is middle-aged. 

If the indicator is \Mercury\, or \Venus\, then the thief is a maiden or a young man, a youth. If they are western, then the indicate the thief is middle-aged.

If the indicator is in his exaltation, the thief is healthy in his limbs. If in its dejection [fall] then it indicates unhealthy limbs. The same if the planet is nearing its exaltation or dejection. It will indicate the same if it conjoins with another planet that is exalted or dejected. 

If planet is within seven days of being under the Sun's rays, the thief has stolen before.

If \Mars\, aspects the indicator, it indicates the thief has experienced imprisonment, agony, misery, and misfortune for prior thefts.

If the malefics do not aspect the Lot of Fortune, the thief has not stolen before this.

If \Saturn\, aspects the \Moon\, and the ascendant, then it indicates the thief has used tricks and has deceived and misled so that he might steal.

If \Jupiter\, is the indicator, then it indicates the thief did not desire the theft and entered the house for something else but he saw an opportunity to steal and did so.

If \Mars\, is the one aspecting the ascendant or the \Moon, then the thief weakened or dug out the wall of the house or broke the lock or copied the key or entered the house by a skylight.

If \Venus\, aspects the ascendant or the \Moon, then the thief entered the house for conversation, and he is a friend of the people who live there, they trust him; but he will steal from them.

If \Mercury\, aspects the ascendant or the \Moon, then it indicates the thief entered the house by a ruse and subterfuge and cleverness and the wish to trouble the people of the house in which he committed the robbery.




