\section{The runaway}
In the matter of a runaway or a fugitive, look at the ascendant and the \Moon\, for the runaway and the \Sun\, and midheaven for the condition of the one seeking the runaway.

If the ascendant and \Moon\, are in tropical signs it indicates the runaway has travelled a distance on land or sea. If in mutable signs, someone else has run away with them. 

If they are in a crooked (short ascension) sign [\Aries,\Taurus,\Gemini,\Capricorn,\Aquarius,\Pisces] then the runaway is confused and strayed from his path or they have been caught. If in a straight (long ascension) sign [\Cancer\, thru \Sagittarius] then the runaway is not confused, will stick to his path and will arrive where he wishes to go. 

If the \Moon\, is not on the equator and is in the first 15° of a mutable sign this is the first time the person has runaway but they will make a habit of it after this. If in the last 15°, the person has runaway before.

If the \Moon\, is in the ascendant, 12th or 11th the runaway is headed East. If in the midheaven,  9th or 8th, they are headed South. If in the 7th, 6th or 5th, they are headed West; in the 4th, 3rd or 2nd, they are headed North.

If \Mars\, is stationary and with or aspecting the \Moon\, then the runaway has shed blood at the place he fled to and has been seized by force or put in chains so he may be sent back to his master or whomever is seeking them.

If \Saturn\, is with or aspecting the \Moon\, then the runaway has raised suspicions or committed a ruse and has fallen in chains because of it. If \Saturn\, is stationary and conjunct the \Moon\, the runaway may strangle themselves unless a benefic aspects, in which case the misfortune will leave them. If \Saturn\, is not stationary when the \Moon\, joins him the runaway has lost any goods he may have stolen before he ran, has wandered and will be seized and sent back to his master in misery and chains.

If the benefics are in the ascendant or aspect the ascendant or are with the \Moon\, then the runaway is truly free. If \Venus\, happens to be in this position the runaway will not be caught but if he is caught and returned he will be content.

If the \Moon\, is increasing the runaway will outrun his searchers; if the \Moon\, is decreasing the runaway will be caught. 

If the \Sun\, is in the sign opposite the ascendant while \Saturn\, is in the 8th sign from the ascendant, the person seeking the runaway will die before the runaway is caught. 

If a malefic is in the midheaven or with the \Sun, then the seeker will have no luck in his search, even he catches the runaway there will be only misery and misfortune to the seeker.

If \Moon\, is in the 7th from the ascendant, without the aspect of a benefic or other relief, and \Mars\, is in the 8th from the ascendant then misfortune and difficulty will reach the runaway and he may die because of it. The same will happen if \Mercury\, (instead of \Mars) is in the 8th and \Mars\, who trines him.

If the \Moon\, is under the \Sun's beams and has not light while \Mars\, aspects the destruction from burning or death by a knife will stop the runaway. To see how the death will come about, look to the sign the \Moon\, occupies as it is USB; if it is human, misfortune will reach the runaway from men; if the signs nature is of a four-footed animal, the misfortune will come from animals; if the sign is in earth, a building will fall on him, if a water sign, he will drown in a flood, and so on with the rest of the signs. If \Mercury\, is with \Saturn\, he will kill himself; if \Venus\, and \Jupiter\, are with \Mercury\, or aspect the \Moon, they will dispel the misfortune, if God wishes, especially if \Jupiter\, and \Venus\, are in their light and their power. 

If the \Moon\, conjoins with \Mars\, in longitude, then beating and imprisonment will reach the runaway; if conjoining in latitude while \Jupiter\, aspects \Mars\, 
  then fear of death will reach him but \Jupiter\, will allow him to escape.
  
If the \Moon\, is in angle with a malefic an unpleasant death will reach the runaway and either his hands or feet will be be cut off. If the \Moon\, is in the midheaven with \Mars\, on his right and \Saturn\, on his left (their signs enclosing the \Moon's sign or their aspects enclosing the \Moon\, by degrees) then the runaway will die by strangulation but if \Saturn\, is on the right and \Mars\, on the left the runaway will be crucified. But if instead the \Sun\, is on the \Moon's left and \Mars\, on the right, the runaway will be burned alive.

The \Moon\, is under the \Sun's rays and ruler of the \Sun's sign does not aspect the \Moon\, then the seeker will die before the runaway is caught. 

If the ascendant, the \Moon\, or the \Moon's dispositor are in a tropical sign (probably \Cancer\, or \Capricorn), the runaway will submissively return to the seeker.

If the \Moon\, aspects both benefics and malefics, if the malefic is square or opposed the \Moon, the runaway will be caught when the \Moon\, reaches the malefic. If he is not caught at that time, he will run into misfortune and difficulties when the \Moon\, reaches the spot where the malefic was. 

If the \Moon\, and the ascendant are injured and not in the aspect of the benefics the runaway, if he does return, will suffer calamity and misfortune. 

If the benefics, in fixed signs, aspect the ascendant and the \Moon\, while they are not also in the aspect of malefics\footnote{The text has `benefics' but that makes no sense; Dykes has  \textsl{``the Ascendant and the Moon are devoid of the aspect of infortunes'' (p305)}}, the runaway will escape. If the benefics are not in fixed signs the runaway will return or be caught but evil and suffering will not reach him and the seeker's anger will be shattered.

If the \Sun\, aspects the ascendent and the \Moon, then it indicates that, whoever runs away or steals goods at that hour, [his master] will triumph over the runaway and the goods and get the better of him. If \Mars\, aspects the ascendant ant the \Moon, he will get power over him soon; if \Saturn\, aspects the pair, he will get power over him after delays and trouble.  If \Jupiter\, is the 7th sign from the ascendant, his master's anger will be dissolved and there will be no disgrace or evil for the runaway; if \Venus\, is in the 7th sign from the rising sign, the runaway is in a place where the gods are worshipped.

If the ruler of the ascendant is in the first decan of a sign or if a retrograde planet is with the ruler of the ascendant or aspects its house, the runaway is nearby. 

If no planet is with or aspecting the ascendant or the \Moon, look to see if the ascendant or \Moon\, are in:
\begin{itemize}[topsep=0em,itemsep=0em]
\item[\Aries] or \Gemini, \Leo, \Sagittarius\, or \Pisces\, as then the master will soon have power over the runaway and he will return submissively of his own accord. If only the \Moon\, is in \Aries\, and the ascendant is in signs other than those just mentioned, the runaway will not be caught

\item[\Taurus] the master will get the better of the runaway but only after effort, trouble, and delay

\item[\Gemini] the first 15° of \Gemini\, and the runaway is not caught within 2 days he will not be caught at all; if the one of the pair is in the last 15° of \Gemini, the runaway will soon be caught

\item[\Cancer] the runaway will soon be caught in a place where the gods are worshipped

\item[\Leo] if in the first half of \Leo, the runaway will be in the house of an important, powerful, strong, and noble person and the master will not get to the runaway except after delay and trouble

\item[\Virgo] capturing the runaway will be difficult as he is fast and constantly on the move

\item[\Libra] the master will catch the runaway but, due to the severity of his anger, the runaway will flee again

\item[\Scorpio] the runaway will be caught in a place where the gods or worshipped or he will return on his own

\item[\Sagittarius]  it the master does not find the runaway with 5 days, he will die and never know where the runaway went

\item[\Capricorn] the runaway will be on the constant move and his master will only find him after delays and trouble

\item[\Aquarius] in the first 10°, he will be caught; if not, the runaway gets away

\item[\Pisces] in the first degrees, the runaway will not be caught, in later degrees, he will not get away
\end{itemize}

If the \Moon\, is in the first half of a mutable sign, this is the first time the runaway has fled; in the last half of a mutable sign, he has fled before.

\subsection{Time unknown}
If the seeker does not know when the runaway fled, use the time at which they were first reported gone and then look at who the \Moon\, first joins.

If she meets first with a benefic and then a malefic, there will be good in the beginning, bad in the end; the reverse if she meets first with a malefic and then a benefic.

If there is a planet in the first 10° of the ascendant the action will go easily; in the later degrees, there will be delays and difficulties.

If \Jupiter\, is in the ascendant and the \Moon\, conjoins \Saturn\, or \Mars, things will go easily but end will be troublesome and bad. If \Saturn\, or \Mars\, is in the ascendant and the \Moon\, conjoined with \Jupiter, the reverse.

If the \Moon\, is under the \Sun's beams (within 15° of the \Sun) the runaway will not be caught or they'll be caught after a delay. Anything begun at such a time will be bad.

If the \Moon\, is in a partile (same degree) conjunction with a malefic the runaway will escape and stolen or lost goods will not be recovered; and every action begun under such conditions will be successful.

\begin{mdframed}[backgroundcolor=cyan!5, rightmargin=1em, leftmargin=1em]
There is a missing text at this point and Dorotheus jumps into describing conditions for a sinking ship.
\end{mdframed}

\textsl{``...or boarding a ship at sea is bad, and it indicates that misinformation and terror will reach him who boards a ship. If it is at the conjunction or at the opposition [of the Sun and the Moon] while the malefics aspect the luminaries from opposition and Mercury is with the malefics which injure the luminaries, then it indicates that whoever boards the ship at sea at that house, the ship will sink and its people and what is in it will be lost....whoever runs away at that hour will soon dies in this running away of his.''}

\textsl{``\{Conjunction and opposition kill and harm everyone and every action, especially if the conjunction or opposition happens to be [at] his nativity. If Mercury is with the malefics, it increases the power for the malefics in what there is of calamities and evil from the malefics.\}''}\footnote{The ``conjunction and opposition'' probably  references  the pre-radix conjunction or opposition of the \Sun\, and \Moon; the \textsl{syzygy} that happened just before the date and time of the chart; in natal astrology it is called the ``pre-natal syzygy'' or SAN.}











