\section{Illness as Qitrinus the Sadwali says}
To know the condition of a patient at the beginning of his illness and for how long it will endure, look at the ascendant and its ruler, the \Moon\, and its ruler, any planet the \Moon\, conjuncts, and the \Moon's dodecatemorion.

If, at the time the patient became ill, benefics were ruling the \Moon\, and the ascendant, or aspecting them and the \Moon's dodecatemorion, or the \Moon\, was with a benefic, then a quick recovery is indicated but if the malefics hold these relationships with the \Moon\, and ascendant, the patient will be ill for a long time.

If the lord of the illness is \Mars, the illness is the result of heat; if \Saturn, the illness is from consumption, coldness and swelling and will be with him for a long time.

If the \Moon\, is afflicted by the malefics but not the ascendant, the illness will harm his body.

If the ascendant is harmed by the malefics but not the \Moon\, then the injury is to his soul and will overwhelm his understanding and blind him or something similar disaster that will ruin his soul.

If the malefics aspect the ascendant without the aspect of the benefics then the patient will die because of the illness, and grievance and pain will in the limb indicated by the sign occupied\footnote{The text says `governed' but that would limit the \Moon\, to \Cancer.} by the \Moon\, or ascendant and if malefics are in this sign or its opposition the pain will be harsher.

To know whether or not he will escape from the disease, look to the aspects of the planets. If you want to know when the condition of the patient will be heavy or light, look to the \Moon. If the \Moon\, by transit or its motion reaches the malefics or they aspect it, the pain will be the heaviest and most severe for the patient and if the aspect is also in the place or terms of malefics it will the condition will be the worst possible. The patient will be released as long as the \Moon\, is in a place and term away from death, as when it reaches the benefics or they aspect it, as then his pain will be lightened and he is helped in his agony.

The \Moon\, reaches its left square after seven days; its left trine after nine days; its opposition after fourteen days; its right trine after eighteen, its right square after twenty-one, and rejoins its original place after twenty-eight days. These days are the best for judgment. If when the \Moon\, reaches one of these places, a malefic conjoins or aspects it, the the pain will be harsher for the patent. If, on these days, the \Moon\, is conjoined or aspected by a benefic, the pain is lightened and the patient is helped.

Judgment is best when the \Moon\, has moved 10 or 40 degrees from where it was when the illness was first begun.  If the \Moon\, in those places, is conjoined or aspected by a benefic, the patient will be released from the illness and recover from it. If the malefics are met with in those places, the patients pain will increase and he will die from the illness and it will be worse if \Mars\, is met with and the chart was drawn by day; if \Saturn\, was met with and the chart was drawn by night, it indicates the severity and harshness of the illness.

If the chart drawn at the beginning of the illness has the ascendant or Moon in a tropical sign the illness will be easier or the patient will recover from it but sometimes there is a relapse. If both the lights are under the earth, it indicates the illness is hideous, severe, but loss and death are not indicated. It is best to look at the aspects of the malefics and benefics to the lights to discover the patient's condition and where he will wind up.

If the \Moon\, reaches \Saturn\, on one of the days declared best for judgment, the illness will increase because of fevers and chills and stretching and extension of the nerves. If it reaches \Mars\, on one of those days, it indicates the illness will increase and be harsher from a hot, strong, sharp fever and the illness will be from excitement and hear and sometimes he will pour forth blood and sometimes this will be of help and it will make him comfortable.

If the \Moon\, is waxing when the person becomes ill and the \Moon\, is in the same sign as the \Sun\, or \Mars, then on the day the \Moon\, reaches the square or opposition to itself, loss and death are to be feared for the patient.  But if the \Moon\, is square or opposed to itself while \Saturn\, aspects, it indicates his recovery and good health. If, instead, the \Moon\, is waning and is with or aspects \Saturn, then the patient will not benefit from \Saturn.

If the \Moon\, is with the \Sun\, or emerges from the \Sun, then, as for him who becomes ill at that hour or whose illness is beginning then, when the \Moon\, reaches that sign or the sign opposite the sign that held the \Moon\, while benefics are with or aspect it, it indicates the patients recovery. If the \Moon\, reaches malefics instead, it indicates the patient's death and loss.

Concerning matters involving the patient, look to the angles. The ascendant indicates the doctor, the midheaven the patient, the descendant, the cause of the illness, the IC his recovery and his medication. If the patient becomes ill when malefics are in the ascendant then he will not benefit from any the doctor's drugs, exertions, or treatments; this is because everything from the doctor becomes an injury. If the benefics are in the ascendant when the patient becomes ill, then he will benefit from the doctor and his treatment will be pleasant.  If a benefic is in the midheaven, it indicates the patient will be treated with a medicine that will be of benefit. If a benefic is in the descendant, the patient will recover from the power of the drug which he drinks, but it will treated him not at all, and it will not be an illness of which he will be afraid, but its treatment will be easy. If there is a malefic in the ascendant and a benefic in opposition, then it indicates that even if the doctor treating him his kind and learned, he will not benefit from it and the reputation of this man and his praise will fall to someone other than his doctor.

If you have the person's natal chart and want to know his condition and death, look to see if the \Moon\, is transiting the sign occupied by his natal \Saturn. If, when he becomes ill, \Saturn\, is with the \Moon\, in its transit and aspects it, then this illness will be severe and one will fear for him. If, at the beginning of the illness, the \Moon\, transits the sign \Mars\, occupies in the natal chart while \Mars\, is with or aspecting the transit \Moon, then the patient will be ill from excitement and intense heat and one will fear for him. If the \Moon\, transits the sign holding both \Saturn\, and \Mars\, in the natal chart and one of them is with or aspecting the \Moon, then it indicates that his illness will be harsher in him and will be heavy and one will fear for him. If the \Moon\, is transiting a natal sign that holds malefics and he reaches a benefic in that sign or a benefic aspects him, then it indicates that this illness will last a long time and will be harsh but he will be released from it. 

For every known nativity, count how many days have passed from birth until the day they became ill. Reduce the result by nines or sevens (for premature births)\footnote{This is essentially modulo math i.e. number of days MOD 9 or 7.}. If there is no remainder after the reduction, it indicates the patient has completed his years and is dead. Since the year has 365 days, reducing by sevens leaves 1 day, reducing by nines leaves 5 days. For a premature birth, count one day for each year that has passed until he became ill; for a full term birth, count five days for each year. Then count the signs between the \Sun\ and \Moon\ in the nativity and the signs between the \Sun\ and the \Moon\ now, and keep the number. Then subtract the number of those signs which are between the \Sun\ and the \Moon\ from the days which have passed of his life till the day he became ill. If nothing is left of the number of these days, then it indicates that this illness is a sever illness or he does not hope to recover or be released from it.

If the \Moon\ is transiting the sixth house of illness or the \Moon's transit has reached the eighth house or the fourth or the sign occupied by the \Moon\ in the nativity, the native will be ill and the illness will be severe and hideous.  If the \Moon\ aspects benefics in these transits, he will escape from the illness. If in its transit it aspects malefics, one will fear for him from the illness. The illness is the worst if at the beginning of the illness the transit \Moon\ is in a sign in the natal chart that holds the deadly star. And the deadly star is the first lord of the triplicity of the fourth because the first lord of the triplicity of the house of the fathers indicates death and the second illnesses and sickness. Some of the lords of the triplicity are called "evil". They are "evil" when the commencement is by day and the lords of the triplicity are diurnal stars and when the commencement is at night and the lords of the triplicity are nocturnal stars. If none of the lords of the triplicity of the house of the fathers is "evil", then it indicates illnesses and a chronic disease. This is the most hideous of what is possible, that according to the transit of the stars the deadly star is with the \Moon\ or aspects the \Moon.

Concerning the matter of the illness consider how the positions of the \Sun\ and the \Moon\ are in the natal chart and when the illness begins. If the \Moon\ is in its left square from her natal place or has reached the transit of the \Sun\ at the start of the illness then it indicates the illness will leave him and he will recover from it. But if it does not reach the transit of the \Sun\ before it reaches the left square, then the illness will stay with him a long time and will not leave except after misery and delay.










