\section{Lot of Wedding (Women)}
The Lot of Marriage for women from \Venus\, to \Saturn\, by day, the reverse by night, added to the Ascendant. Planets in the the lot or square to it become ``the indicator'' of the marriage.

If \Mars\, is the indicator the women will marry a number of men in succession and ``play the whore with men.''

If \Saturn\, rules the lot and is in the 7th it indicates she will marry an older relative. If the woman is a slave or servant then she marries her master.

If \Mars\, rules the lot, she marries a man ``that will not be known'' who has a \Mars\, profession.

If \Jupiter\, rules the lot, she marries a man who is known, is famous in the towns and cities.

If \Venus\, rules the lot, there will be a marriage with ``joy from wine.''

If \Mercury\ rules the lot, the marriage will be made with deceit and quarrelling, especially if \Mars\, aspects.

\subsection{Indications from Venus}
\Venus\, in a bad place in the charts of men or women indicates a ``disgraceful marriage.'' If a malefic aspects \Venus\, its malice is mitigated if \Jupiter\, also aspects \Venus. 

\Jupiter's aspect of \Venus\, in a man's chart indicates benefits from women; in a woman's chart, benefits from men.

If \Venus\, is in a two body or two figured sign then the person will have more than one marriage.

\Venus\, and \Mars\, in mutual reception by domicile or \Mars\, with, square, or opposed to \Venus\, indicates, for the person, ``disgrace, debauchery and destruction.''

If \Venus\, is with \Mercury\, and \Mars\, the person ``will have no stability in marriage, but he will rejoice in this woman one time, in that woman another time.'' If they are in the midheaven or if \Venus\, is in the midheaven and aspected by \Mercury\, and \Mars\, the man will be one who befriends women\footnote{Dykes says he ``will be of those befriending the women of [other] men'' (p123).}. If the planets aspecting \Venus\, are eastern his befriending will be public. If \Jupiter\, aspects one of \Venus, \Mercury, or \Mars\, at the same it mitigates the harm done to the woman. If \Venus's triplicity rulers are in the midheaven ``her debauchery will occur publicly and with renown.''

If \Jupiter\, and \Venus\, are both in bad (cadent) places  then ``disgrace, debauchery, and a bad reputation are indicated.''

If \Venus's first triplicity lord is in a good place and the second in a bad place it indicates then the women's condition is good in the beginning but worse in the second part of life.\footnote{Dorotheus assigns the three triplicity lords to three stages of life: beginning, middle, end.}





