\section{How many wives will he marry?}

The number of planets between \Venus\, and the midheaven indicate the number of wives but ``wherever you find \Saturn, then know [his] coldness and distance; wherever you find \Mars, [his] death unless a benefic aspects it.'' If \Venus\, is cadent from the midheaven, the man has little constancy toward women.

For women, count the number of planets between the midheaven and \Mars, unless \Mars\, is in the midheaven, then count to \Jupiter.  If \Mars\, is in the 7th the woman has little constancy toward her husband.

The Lot of Happiness and Wedding is counted from \Venus\, to the degree of the 7th (the reverse by night) and projected from the Ascendant.  If the lord of the lot is in a bad place and \Venus\, is USB and aspected by malefics the person will never marry. If a malefic is in the lot or aspects the lot the person will marry disgraced women and one from whom there is no good.

The wedding is timed by a transit of \Jupiter\, or \Venus\, to the square, opposition, or trine of the lot unless \Saturn\, is also square or trine the lot, in which case the marriage will not occur or, if it does, it will not last long.

Marriage is possible whenever \Jupiter\, transits radix \Venus. And sometimes a \Saturn\, transit, if he is well-placed and connected with the lot in the radix, can time a marriage, especially if \Jupiter\, aspects him.

If multiple wives are indicated, marriage can occur whenever \Venus\, transits or aspects her own house but the marriage will be neither stable nor suitable. The same if \Venus\, and \Mars\, are in aspect.

The marriage partners suit each other and are in agreement if:
\begin{itemize}[topsep=0em,itemsep=0em]
\item both the man and woman have their Ascendants in the same angle, or 
\item either one has a light in the ascendant or midheaven, or 
\item the \Moon\, in one chart is in the place of \Venus\, in the other or vice versa especially if the two \Moon's are in trine
\item a light in one chart is in the same sign as a benefic in the other's chart
\item both have all their benefics in angles
\item each have their lot\footnote{Not sure if this means the Happiness \& Wedding lot or the Lot of Fortune. Dykes, in a footnote to 2.5, says it refers to the Lot of Spirit.} in the same sign
\end{itemize}

Incompatibility or problems are indicated if:
\begin{itemize}[topsep=0em,itemsep=0em]
\item the sign occupied by a malefic in one chart is the same as the sign occupied by the \Moon\, in the other chart indicates ``injury and little agreement'' between the couple
\end{itemize}