\section{Number of Children}
\subsection{Indications from the Moon and Venus}
If the \Moon\, and \Venus\, are in \Cancer\, or \Capricorn\, or their triplicities (\Scorpio, \Pisces, \Taurus, \Virgo), the one in the ``better position'' becomes the indicator of children. If they are not in these signs use \Jupiter\, as the indicator.

If the indicator is in the midheaven, ascendant, or Fortune the person will have children while they are young. 

If the indicator is in the 2nd, 8th, 4th, or the lot of wedding then the person will have children in his middle or later years.

\subsection{Indications from Jupiter}
If the indicator of children is \Jupiter\, and he is in a good place but USB, the person ``will have children but they will not live.''

Identify which of \Jupiter's triplicity rulers is strongest. If it is in the 10th the person will have one child or four. If it is in the 7th then the person will have seven children or one, especially if \Aries\, is the sign on the 7th.

If the triplicity ruler is in the 9th or 3rd, count the number of signs between it and the Ascendant and that will be the number of children. Modify the number by:
\begin{itemize}[topsep=0em,itemsep=0em]
\item adding to it the number of planets in the signs counted
\item increasing it if \Jupiter\, and \Venus, are in the signs counted
\item if one of the signs is double-bodied, double the count found from it
\item if \Saturn\, or \Mars\, are in the signs counted and those signs are in good places they increase the number of children except the extra child will be expelled, especially if the malefic is in the 7th or 4th. 
\item if \Saturn\, or \Mars\, are in the signs counted and those signs are in bad places, a child will die
\end{itemize}






