\section{Lots of Male and Female Children}
The Lot of Male Children is counted from \Jupiter\, to the \Sun\, by day, from the \Sun\, to \Jupiter\, by night and projected from the Ascendant.

The Lot of Female Children is counted from the \Moon\, to \Venus\, by day or from \Venus\, to the \Moon\, by night and projected from the Ascendant.

The condition of each lots ruler is used to determine whether the person will have more male or female children.

The person will have few or no children as:
\begin{itemize}[topsep=0em,itemsep=0em]
\item \Saturn\Opposition\Mercury\, indicates the death of children
\item \Venus\Opposition\Saturn\, without the aspect of \Jupiter\, indicates few children, or, sterility if \Saturn\, also aspects the \Moon\, while she is in a tropical (\Aries,\Cancer,\Libra,\Capricorn) sign with a malefic
\item the \Moon\, square a malefic indicates there will be no children
\end{itemize}

The person will suffer grief and sorrow due to children if:
\begin{itemize}[topsep=0em,itemsep=0em]
\item a malefic squares the lot, indicates the loss of children
\item the lot is in the 12th or 6th aspected by \Saturn, which indicates the death of children
\item \Jupiter\, square or opposed to a malefic or in the 7th or 4th with a malefic indicates the death of children, especially if \Jupiter\, is ``without light''\footnote{Not in the same hemisphere above or below the horizon as the \Sun.}
\item the \Sun\, and \Saturn\, in the same sign indicates grief related to having children
\item \Saturn\, injuring \Venus\, without the aspect of \Jupiter\, indicates grief over children or they will have children but not enjoy them especially if \Saturn\, is also aspecting the \Moon
\item \Jupiter\, cadent indicates a child but they will lose their parents.
\end{itemize}

If \Jupiter\, and \Mercury\, are not injured there will be ``an abundance of children''. If the two are USB or in their fall then there will be no children or if there are, they will die.

The planets aspecting the midheaven, its sign and aspects and the sign following the midheaven indicate male and female children.

The likelihood of children can be judged from the strength and condition of the 5th house and its lord. If the ruler is cadent and neither \Jupiter\, nor \Venus\, aspect the 5th while malefics do, there will be few children and their lives may be brief. If at least one benefic aspects the 5th the person will have some children. If the lord of the 5th is in a good place, aspecting the midheaven, there will be an abundance of children and good because of them.

