\section{Planets in the same sign}
\begin{description}[style=multiline,leftmargin=1.5cm]
\item[\Jupiter,\Mars]
``indicates leadership and property and honor in metropolises and cities, and he will be one of the judges for communities, abounding in work.

If they are both in the house of one of them, then he will be powerful, steadfast, celebrated in arms, and the like''

\item[\Jupiter,\Sun]
if \Jupiter\, is USB ``it indicates decrease of everything. If it [\Jupiter] is eastern\footnote{``Eastern'' here probably means that \Jupiter\, is at least 15° degrees from the \Sun, and rises ahead of it.}, it indicates good fortune and property and gain and luck to his parents and joy in [his] children''

\item[\Jupiter,\Venus]
``he will be one of those who will be brought up in honor and wealth, he will love the generality of people, [he will be] merciful, good in [his] intention, good in [his] appearance, pleasant in the eyes of chiefs and nobles, desirous of good and of fame; property and leadership will come to him because of women and houses of worship, and [he will be] good in [his] marriage and children.

If a malefic is \textsl{[not]}\footnote{There is no `not' in the text but the statement doesn't make much sense if it is excluded; malefics between the two would be more apt to cause conflict or separation than love and a warm welcome.} between these two, then he will be beloved and received wherever he may be; thus [also] in the nativities of women.

If \Jupiter\, is with \Venus\, in a strong place and the \Moon\, and \Mars\, aspect these two, then a disgusting and shameful affair involving one of his relatives will be added.''

\item[\Jupiter,\Mercury]
``he will be an expert in law, victorious in words, and perfect in reasoning and intellect, learned, the raiser up for the great among the people, and some of them will be secretaries for the more powerful grandees or kings''

\item[\Jupiter,\Moon]
``indicates an increase in property, dignity, and good fortune. If \Jupiter\, is powerful [and] eastern, there will be good for the native from his fathers. If the \Moon\, is less in degrees and \Jupiter\, is not bright, then this will decrease the good fortune of the native''

\vspace{0.5em}\hrule
\item[\Mars,\Sun]
``indicates the swiftness of his father's death. It is worse and more terrible if it is in a cardine or what follows a cardine---it indicates pain for the native an aches, and he will be envious, squandering his father's property, and iron or fire will fall on him; and he will be mixed up in his opinion[s and] will have no constancy in them''

\item[\Mars,\Venus]
``indicates quarreling and disaster and injury because of women. If the sign is tropical (\Aries,\Cancer,\Libra,\Capricorn), then he will have intercourse with a bad woman, and however it may be quarreling will come to him because of women, and he will be excessive in sexual intercourse; predict similarly in the nativities of women that they will be disgraced in sexual intercourse''

\item[\Mars,\Mercury]
``he will be a liar except that he will be reasonable, intelligent, learned, desirous of culture, [and] he will love arguments. 

If \Jupiter\, aspects it, [he will have] praise for that. 

If it is \Venus, then [it will be] like this and he will be strong in love for his children. 

If \Saturn\, aspects, then there is no good in it because he comes to hatred and defects; and it will punish this native

If \Mercury\, and \Mars\, are thus USB in a cardine and they aspect \Venus, then he will be misleading in his intention and thought, [and] the leaders of thieves will be opposed to him, [and] he will act perfidiously in pleasure.

If \Jupiter\, aspects, the evil will desist from him.

\item[\Mars,\Moon]
``indicates the shortness of his survival and a terrible death and a chronic illness, and some of his flesh will be cut with iron, and it indicates misery for his mother. If they are both in a cardine, then he will be relaxed in his work [and] refractory, and in addition to this it indicates injury

\vspace{0.5em}\hrule
\item[\Sun,\Venus]
If ``western in nocturnal nativities and eastern\footnote{``Western'' most likely means ``setting after the \Sun,'' ``Eastern'', rising before the \Sun.} in diurnal nativities, then he will be praiseworthy [and] welcome''

\item[\Sun,\Mercury]
whether \Mercury\, is east or west of the \Sun, the person ``will be gentle, a scribe, [and] he will have status for his culture and reasoning, and he will be a chief and will benefit others''

\vspace{0.5em}\hrule
\item[\Venus,\Mercury]
``he will be lazy in [his] jobs, desirous of joy and pleasure, abounding in women, adorned with culture and words, loquacious in poetry because he will compose pleasing [and] beautiful words, but he will be disconcerted because of intercourse with women so that his pleasure and his desire will be in slave girls.

If both are in the ascendent, then it is better and more secure for their strength, or profit and nobility will come to him from women if \Jupiter\, aspects it''

\item[\Venus,\Moon]
``he will be great in [his] appearance, good in [his] children, joyful, fortunate, but he will have no constancy in [his] marriage [and will be] desirous with respect to women other than his won, and the wives of some of them will do similarly in having intercourse with other than them''

\item[\Mercury,\Moon]
``he will be praiseworthy in [his] reason and understanding, perfect except that he will be a liar [and] will not be constant with respect to an affair.

If a benefic aspects these two, this evil will diminish and it indicates for his mother good except that she will be disgraced by men.

If the \Moon\, is greater in degrees than \Mercury, then it will be good because, if the \Moon's degrees abound, it accomplishes the strength of the planets which it is leaving because the \Moon\, is nearer the earth than the planets [are]''

\end{description}