\section{Profections}
\begin{quote}
\mn{4.1-2}\textsl{When a native is born, the lord of the year is the lord of the house [ascendent] in which the native was born. Thus count from the ascendent a year for each sign until you reach the year which you desire; the lord of that house is the lord of the year.}
\end{quote}

\begin{table}[h]
\small
\center
\begin{tabular}[c]{|c|r r r r r r r r r|}
\hline
Place & \multicolumn{9}{|c|}{Age on Birthday}\\
\hline
1st  & 0 & 12 & 24 & 36 & 48 & 60 & 72 & 84 & 96 \\
2nd & 1 & 13 & 25 & 37 & 49 & 61 & 73 & 85 & 97 \\
3rd  & 2 & 14 & 26 & 38 & 50 & 62 & 74 & 86 & 98 \\
\hline
4th  & 3 & 15 & 27 & 39 & 51 & 63 & 75 & 87 &  99 \\
5th  & 4 & 16 & 28 & 40 & 52 & 64 & 76 & 88 & 100 \\
6th  & 5 & 17 & 29 & 41 & 53 & 65 & 77 & 89 & 101 \\
\hline
7th  & 6 & 18 & 30 & 42 & 54 & 66 & 78 & 90 & 102 \\
8th  & 7 & 19 & 31 & 43 & 55 & 67 & 79 & 91 & 103 \\
9th  & 8 & 20 & 32 & 44 & 56 & 69 & 80 & 92 & 104 \\
\hline
10th  &   9 & 21 & 33 & 45 & 57 & 70 & 81 & 93 & 105 \\
11th  & 10 & 22 & 34 & 46 & 58 & 71 & 82 & 94 & 106 \\
12th  & 11 & 23 & 35 & 47 & 59 & 72 & 83 & 95 & 107 \\
\hline
\end{tabular}
\caption{Profections}
\end{table}

Dorotheus calls it the ``transfer of years'' but the method described is commonly called \textsl{profection}. The radix chart is turned at the rate of one whole sign per year. The domicile lord of that sign becomes the ``lord of the year.'' Essentially, the zodiac signs ``turn'' at the rate of one per year, rising up so that a new sign occupies the first house on each successive birthday such that, on your 1st birthday the sign occupying the radix 2nd house moves to occupy the 1st place, on your 2nd birthday, the sign occupying the radix 3rd moves to occupy the 1st place, and so on until at the end of 12 years the original ascendant sign is back occupying the 1st place, and again at the end of 24 years, 36 years, etc.

\begin{quote}
\mn{1.4}\textsl{[A]nd the beginning of the year is always when the \Sun\, enters the beginning of the minute in which it was on the day of the native's nativity.}
\end{quote}

The new year, for each birthday, begins when the \Sun\, holds the same degree and minute it held at birth so if you are born on July 13 with the \Sun\, at 20\Cancer 30 then each ``new year'' for you will begin exactly when the \Sun\, re-occupies that degree on your birthday.

\begin{quote}
\mn{1.3-4}\textsl{Look at the lord of this sign\footnote{The profected sign.}, whether it is a benefic or a malefic, and in the base-nativity how its position was and in which foundation it was. From the base-nativity is known what is concerning him [the native] at the beginning of the year}
\end{quote}

The general condition of the year depends on the condition of the lord of the year as it is found in the radix. We are told that if the lord of the year is:
\begin{itemize}[topsep=0em,itemsep=0em]
\item western \textsl{[from the \Sun?]} then ``misfortune will reach the native''

\item USB (invisible) by being conjunct the \Sun\, or opposite the \Sun\, in \textsl{curtailed passage} and retrograde there will be misfortune but if the planet is direct in motion ``it will be better for him and it will be good''

\item in his own domicile or if the \Sun\, or \Moon\, aspect the profected ascendant from a sign of the same triplicity there will be no harm

\item in the sign of an enemy, the person ``will be sick, and injury and loss with respect to his property will reach him''
\end{itemize}