\section{Death}
\begin{quote}
\mn{1.143}\textsl{Now I will make clear to you the matter of death.}
\end{quote}

\subsection{The 8th}

Identify\mn{1.144-45} the sign and its nature: watery, dry, human, quadruped, or wild. Then identify ruler of the sign and the planets aspecting the sign.

If \mn{1.146-9} \Saturn\, rules the 8th and he is in the West\footnote{Dykes has this ``as in an alien place'' saying that ``western'' does not make sense in this context. By an ``alien place'' I'm assuming he means the planet has no dignities in the sign it is in. Although, I think ``in the West'' here might be equivalent to being in the 7th which indicates ``foreign lands'', so someone dying in a foreign country.}, then \textsl{``this native will die in other than his own land''} and if \Saturn\, is in a moist sign the person \textsl{``will die in the water or the belly of a sea monster or a fish,''} or if \Saturn\ is an earth sign, \textsl{``then the native will die at the peak of a mountain''} or if the \Sun\, is with \Saturn, \textsl{``then this native will fall from a high place and will die.''}

If \mn{1.150-153} \Mars\, rules the 8th, \textsl{``then thieves will fall upon this native and kill [him] or [his] enemies will kill him in a fight or he will burn in a fire or an animal from among the earthy animals will bite him or lions will devour him.''} If the \Sun\, is with \Mars, \textsl{``then this will reach him from the anger of kings or the anger of a great man so that he will be killed or crucified on a post, or his middle will be cut with a sword, or a lion and a tiger will slay him, or animals or hogs will vie [with him]''} and if \Mars\, is not in one of its own places, \textsl{``then he will die in exile from his land''} but if \Mars\, is in one of its own places, \textsl{``then this native will die because of women or by means of poison and drinking a drug.''}

If \mn{1.154} \Mercury\, is the lord of the 8th, \textsl{``then he will die from the anger of kings'.'}

If \mn{1.155-7} the ruler of the 8th is not in one of his own places and is impeded by a malefic who is in the 8th, \textsl{``then this native will die on a journey''} but if the lord of the 8th is in one of his own places, \textsl{``then this native will die in his own land and in his place and among his people.''} But if the lord of the 8th is benefic and impeded, \textsl{``then the death of this native will also be thus, but his death will be better for him.''}

\subsection{Lot of Death}
\textsl{``Some of them learned in the stars''} \mn{1.158} counted from the \Moon\, to the 8th and \textsl{``then cast out from \Saturn,''} and judged the native's death from the sign the lot fell in and ruler of that sign.

\subsection{Planet first to the Descendant}
\begin{quote}
\mn{1.159}\textsl{``Some of them looked at that planet which reached to the degree of the seventh, and not in the casting [of rays], but they saw which of the two would be more quickly cadent in the West so that from that one they might judge death for him, if God wills.''}
\end{quote}
Believe he means we should look at the first planet that will move, by primary motion, across the Descendant (cusp of the 7th) into the 6th (a cadent place) and judge the manner of death by that planet's condition in the radix.

\subsection{A Difficult Death}
\begin{quote}
\mn{1.165}\textsl{If \Mars\, is in the tenth but not in the cardines while the \Moon\, is in a cardine, the seventh, and the malefics aspect the \Moon, then enemies and thieves will kill this native.}
\end{quote}

Believe he is saying that if the \Moon\, is angular in the 7th house and \Mars\, is in the 10th sign but not the 10th house i.e. cadent in the 9th house, then the native will be killed by enemies and thieves; possibly as such a planet would square the \Moon. For example, if the Asc is in 10 \Taurus\, and the MC in 15 \Aquarius\, then \Mars\, at 12 \Aquarius\, would be in the 9th house and in square to a \Moon\, in the 7th at 12 \Scorpio.

\begin{quote}
\mn{1.166}\textsl{ If the malefics are rising after the seventh sign or are aspecting it from the seventh (it will be worse for this [native] if the malefics are in cardines), then this native will die a difficult death.}
\end{quote}

This possibly means that if the \Moon\, is in the 7th and a malefic is in the 10th, 9th, or 8th (rising after the 7th) or in the 1st (7th from the 7th and so in opposition to the \Moon) then the native will have ``a difficult death'' and the worst would be if the malefic was in the 1st or 10th. I'm assuming primary motion is meant here based on his use of ``rising after'' which can only happen by primary motion.

\subsection{Triplicity Rulers of the 4th}

Look \mn{1.167-70} at the triplicity lords of the 4th, the first indicates death and the second, chronic illness. If both are together in a bad place, judge the native will have a difficult death. If the first triplicity lord is in the 4th or in the 7th, \textsl{``then this native will die and not one of men will appear to see him, and they will not know how he died, and they said that this man will be named as a messenger.''}

If \mn{171} the 2nd tripllicity lord is in the 7th, \textsl{``then this native will be chronically ill [and] miserable; if it is aspecting the house of life, it will be worse for him.''} 

\subsection{Indications from the 7th}

If \mn{172-3} the ruler of the 7th is a malefic and it is USB, \textsl{``then this native will die from [his] slaves or from a matter which no one knows. If this planet is seen in the East, then this native will die publicly, but if it is retrograde, then this native will die from a drug in which [there is] no good, and his suffering will be prolonged.''}

If \mn{1.174} the 7th sign is a human sign, \textsl{``then he will die because of men, and if it is one of the watery signs, then he will die because of water, and if it is one of the quadruped signs, then he will die because of quadrupeds or lions will eat him.''}

If \mn{1.175} the malefics are with the \Moon\, or the other malefics are aspecting the \Moon\, from the 7th, then he will die from surgery.

If \mn{1.176} the \Moon\, is in a new sign when it shines from the \Sun\, and...is aspecting the \Sun\, from the 4th or the 7th but not aspecting the \Moon, then this native will kill himself.

If \mn{1.177} the \Sun\, is eclipsed in the 7th or the \Moon\, is passing from a degree which aspects the degree the \Sun\, is in\footnote{\Moon\, is separating from the eclipse degree?}, \textsl{``then this native will die in fire or in water, and many people will die with him.''}

If \mn{1.178} the ruler of the 7th is in a place in which [there is] no good or it is in the 10th while the malefics are with the \Moon, \textsl{``then this native will fall from a high place and will die from it.}

If \mn{1.179} the lord of the lot of the 7th\footnote{Dykes thinks this is the Lot of Eros which is taken from Fortune to Spirit and projected from the Asc in a diurnal chart, from Spirit to Fortune in a nocturnal chart. (p220n112} is with the lot of luck\footnote{Dykes thinks this is the Lot of Fortune (p220n113)} and the malefics are determinative, then he will die because of his friends.

If \mn{1.180} \Venus\, is in the 7th house and the \Moon\, is peregrine and with the malefics, \textsl{``then the death of this native will be because of a woman who has had many husbands, [but] then they died.''}

If \mn{1.181} \Jupiter\, is like \Venus, \textsl{``then he will die because of [his] children or from his good name and good reputation which they will be envious of.''}

If \mn{1.182} \Mars\, is like \Venus, \textsl{``then [he will die] because of his brothers.''}

If \mn{1.182} the \Sun\, is like \Venus, \textsl{``then he will die because of his mother and his ancestors.''}

If \mn{1.183} the \Moon\, is like \Venus, \textsl{``then he will die because of his mother and his father's wife.''}



