\section{The Cardines (Angles)}
\begin{quote}
\mn{1.234-235} \textsl{Now I will make clear to you the matter of the cardines. Look concerning these four cardines:}
\end{quote}

\begin{itemize}[topsep=0em,itemsep=0em]
\item[1st] for the appraisal of the native
\item[10th] for the matter of children\footnote{Children are usually signified by the 5th} and of work
\item[7th] for the matter of women and marriage
\item[4th] for old age and the end of life
\end{itemize}

\textsl{``And the matter of the body and of property is known from the prorogation\footnote{The term used in the text for directing the angles, planets, or lots according to their right/oblique ascensions (primary directions) See \hyperref[sec:longevity]{Book III Longevity Example}.} of the degrees and [their] varieties.''}

The \mn{1.236} ascendent gives the matter of youth, it is the place where the \Sun\, rises from the water, and the darkness in their eyes is raised up for the people of the world, and sheds light on the eyes of the messengers who sent them forth to creation.

After \mn{1.237} youth, the 10th and its gift [lasts] until the body of this native becomes warm and hair grows on his pubic area and he loves sexual intercourse.

From \mn{1.238} the 7th will be the gift of old age, and it will diminish the strength of this native for sexual intercourse [so that] the native will be insignificant in this, and the \Sun\, sets and darkens [their] eyes.

From \mn{1.239} the 4th is known the gift of death.

If \mn{1.240} the planets are luminous in these four angles, then this native will attain good; if they are darkened, then [there will be] no good in it.

The 4th book of Dorotheus on the revolution of the years of the nativity is completed by the praise and grace of God.

The 5th book, about interrogations, follows it.

