\section{Is the Person and their Mother Free or a Slave}

First, examine the \Moon's condition. 

If the \Moon\, is in the 12th or 6th place and:
\begin{itemize}[topsep=0em, itemsep=0em]
\item the first triplicity lord of the place is in a bad place, the native is a slave, unless
\begin{itemize}[topsep=0em, itemsep=0em]
\item it is a night chart and the \Moon's second and participating triplicity lords are in good places, or
\item it is a day chart and the first and second lords of the \Sun's triplicity are in good places
\end{itemize}
In which case the person is born free but his parents are poor.
\end{itemize}

If the \Moon\, is in the last degrees of a sign, the mother is of bad descent unless:
\begin{itemize}[topsep=0em, itemsep=0em]
\item  \Jupiter's aspect removes the misery, which happens even if \Jupiter\, is badly placed\footnote{The wording in the original is confusing; this appears to be the author's intent.}, or

\item the \Moon\, is with \Venus\, in one of \Venus's domiciles in which case ``the evil'' disappears.
\end{itemize}

If a malefic is in one of the \Moon's angles\footnote{If either malefic found in the 4th, 7th, or 10th place from the \Moon.} and \Mars\, (in a day chart) or \Saturn\, (in a night chart) aspect the \Sun\, or \Moon\, without \Jupiter\, also being in aspect, the person will be a servant. And his condition may be worse if the \Moon\, is in a feminine sign and worse yet if \Venus\, is also injured.

If the \Sun\, and \Saturn\, are in the 6th, 12th, 8th, or 4th then the father's condition is unfortunate.

If the \Sun\, and \Moon\, are in the terms of benefics and aspect the ruler of the place they occupy then the parents condition is good as will be the person's survival and upbringing. The conditions will be even better if  the \Sun\, or \Moon\, is angular or it one rules the Lot of Fortune.

If the \Moon\, is angular or succedent and being overcome\footnote{The text has ``supervised'', Dykes translation has ``looked down on'' which he equates with \textsl{overcoming} i.e. the malefic in the 10th place from the \Moon..} by a malefic, the person will be struck down even if he is free. There is destruction if the \Moon\, is with one malefic while there other overcomes them.

In a nocturnal chart, if the \Moon\, is in the 7th or 4th and in the aspect of a malefic, destitution, slavery and difficulty is indicated for the persons livelihood.

The Lot of Fortune or its ruler in another's terms in the 6th or 12th  indicates service.

If the \Moon\, in a nocturnal chart is in a masculine sign while the Ascendant is in a feminine sign or, if in a diurnal chart, the \Sun\, is in a feminine sign while the Ascendant is in a masculine sign, the person will be like a slave.

Check the \Moon's, \Sun's and Ascendant's term rulers to see if they are feminine (\Saturn, \Venus\, \Moon) or masculine (\Sun\, \Jupiter, \Mars)\footnote{This is strange for a number of reasons (1) Dorotheus does not connect the state to the condition of being free or a slave, (2) the \Moon\, and the \Sun\, do not rule any of the the most commonly used Egyptian terms, (3) \Saturn\, is usually considered a diurnal and therefore masculine planet although Dykes says there are other instances of \Saturn\, being deemed feminine found in Sahl and Theophilus. Although it could just be a transcription error.}.

The \Moon\, with the malefics without the aspect of a benefic indicates slavery.

A malefic in an angle or \Mars\, aspecting the \Moon\,  while the \Moon\, is moving to conjunct \Saturn\, indicates slavery. The same if \Saturn\, is aspecting the \Moon\, while she is moving to conjunct \Mars.

If the \Moon\, is in the end of a sign and aspected by \Saturn\, or \Mars\, the person may be aborted or his birth made hard; unless \Jupiter\, or \Venus\, also aspect the \Moon, in which case the person is born but raised by strangers.

If the first lord of the Ascendant's triplicity is cadent and opposed by the \Moon\, while the \Sun\, is in a bad place, the person's parents are slaves.

\subsection{Indications from the SAN}

Note the degree of the SAN\footnote{SAN is an acronym for \textsl{Syzygyium Ante Nativatem} which refers to the \textsl{syzygy}, the whole-moon (conjunctional) or full-moon (preventional) immediately before birth which may also be called the \textsl{lunation} before birth.} and the 1st and 2nd triplicity lords of its sign. 

If the 1st lord is in a bad place and the 2nd in a good place, the person will be born into slavery but freed in later life.

If the 1st lord is in a good place and the 2nd in a bad place, the person is born free but will be reduced to poverty, contempt and service in his later years.

If both triplicity lords are bad places, the person will being and end life as a slave or servant.

If both triplicity lords are in good places, the person will begin life free and end it free.

If a malefic is with the SAN and the other malefic is in aspect, the person ``will experience his fate and evil will overcome him.''

If the SAN's term lord is in a bad place or the 7th or the 4th the life will be lived in slavery and poverty.

If the SAN is in a bad place and aspected by malefics but it is also aspected by a benefic and its term lord is in a good place then the person's father if of noble birth and his mother is of poor lineage.

\subsection{Escape from Slavery, Service, or Poverty}
Indications that a person will be freed from any indicated slavery, service, or poverty are:
\begin{itemize}[topsep=0em, itemsep=0em]
\item \Jupiter\,  in any angle, in any sign except \Capricorn, regardless of being with malefics or benefics. And if \Jupiter\, aspects the \Moon, ``the pains of slavery are completely loosened for him.''

\item \Venus\, in an angle, free of the malefics

\item \Venus\,  in the 7th with the \Moon

\item the \Sun, \Moon, and \Mercury\, in angles
\item the \Sun\, and \Moon\, in the same triplicity
\item the \Moon\, angular in \Taurus\, or \Cancer\, free of the malefics or aspected by both malefics and benefics
\end{itemize}

\subsection{Effect of Jupiter}
If \Jupiter\, is with or square the Lot of Fortune the person escapes slavery but if \Jupiter\, aspects the Lot of Fortune while both are  in bad places the person will be freed from slavery but will not escape servitude.

If \Jupiter\, is in the 2nd or 8th the person will experience what is like slavery and worse if \Jupiter\, is in the 6th or 12th.






















