\section{Lot of the Mother}

Calculate the Lot of the Mother, by degrees, in a daytime birth, from \Venus\, to the \Moon; for a night chart, from the \Moon\, to \Venus, and add the difference found to the Ascendant.

The parents are of different nationalities if:
\begin{itemize}[topsep=0em, itemsep=0em]
\item the \Sun\, and \Moon\, are both in tropical signs (\Aries, \Cancer, \Libra, \Capricorn), especially if the malefics are conjunct, square, or in opposition to them

\item the lights don't aspect each other or the Ascendant

\item one of the lights is below the earth, the other above with malefics

\item the Ascendant is in a tropical sign with one of the lights and there are other planets with them, especially a malefic
\end{itemize}

\subsection{Separation of Parents}
The \Sun\, or \Moon\, in the 7th place indicates the parents are separated and, if the light is in the terms of a malefic, the indicated parents property is squandered.

\Mars\, or \Saturn\, conjunct, square, or opposed to the \Sun\, without any aspect from the benefics indicates the father's property is squandered. If the \Moon\, is in the same position, the mother's property is squandered. And if the parents are separated when the person is young he may be a needy orphan.

\Saturn\, angular, especially in the 7th,  with \Jupiter\, cadent and not aspecting \Saturn\, indicates separation of the parents. The same if \Mars\, is in the same condition and \Saturn\, and \Venus\, in the same condition as \Jupiter.

The two lights opposed to each other across the 6th-12th axis, or both together in the 6th or 12th, indicates the parents separation.

The lot of the father and mother together in the same place indicates separation of the parents as do malefics aspecting the lots.

Separation is also indicated if the two lights do not aspect each other or the Ascendant.

``If you find the two lots, each one of them, in a sign at its term[s], and the malefics are also injuring them from the sign, then this is an indicator of the destruction of what is between the parents.\footnote{Can't make head or tails of this. Dykes has ``And if you found the two Lots, each of them in a sign separated [from the other]\textsl{[in aversion]}, and the infortunes also harming them both from the sign\textsl{[possibly the 4th or 7th is meant]}, then that is an indicator of the corruption of what is between the parents.'' I am wondering if it might mean if you find the lots in the terms of a malefic and also harmed by the same malefic.}.''

\subsubsection{The 4th Place}
The \Moon\, and \Venus\, both aspecting the 4th indicates ``an increase of good and a goodness of condition'' for the mother.

If the \Sun, \Jupiter, and \Saturn\, are in the 10th in opposition to the 4th ``it indicates praise of the father and the goodness of his condition.'' 

If both the above situations occur at the same time ``then judge for his two parents together good fortune and wealth and fame.''

Misfortune, misery, and slavery for the parents is indicated if \Mars\, and \Saturn\, are in the 4th without a benefic or if the malefics square or oppose the 4th.

The \Moon\, in the 4th indicates evil for the mother; the \Sun\, in the 4th, evil for the father.



