\section{Magnitude of Fortune}

Examine the distance of the triplicity ruler of the sect light from the angles using equal (oblique ascension) degrees and judge the magnitude of the fortune according to the following:
\begin{itemize}[topsep=0em,itemsep=0em]
\item[0-15째] the person ``will be most perfect in fortune and property''
\item[15-30째] good fortune and property, ``the nearer to the degree of the cardine, the higher it is for his rank in emience and fortune''
\item[30-45째] the person ``will not be known,...and middling in property and fortune''
\item[45째+]  the person ``will be needy [and] miserable''
\end{itemize}

``[You] should have these degrees in [the risiing-time of] the ascendents because degrees are equal, thirty [to a sign], bu the ascendents are not equal because some of them are crooked and some straight. And the crooked ones ae quicker in rising, the straight ones slow in rising; and their rising-ties in every region and clime is not the same because the region of the vicinity of the North is long and square while the vicinity of the Suth is low [and] excessive[?].''

There is no good or pleasure for the person in his property, even though he thinks it might be good and increase, if the triplicity rulers of the \Sun\, are in bad places and those of the \Moon\, are found in good places. 

If the \textsl{[triplicity]} rulers of both the lights are in bad places look to the Lot of Fortune.

\subsection{Lot of Fortune}
By day, count from the \Sun\, to the \Moon\, in the order of the signs and add the result to the Ascendant. By night, count from the \Moon\, to the \Sun. Judge according to location of the lot, its ruler, and the aspects they are involved in.

\noindent\textsc{Bad Indications:} \hfill \\
If the lord of the lot is cadent or averse to the lots.

If the lot and its lord are in the 6th or 12th, USB, or aspected by malefics.

By day, \Mars\, conjunct, square or opposed to the lord of the lot.

The lord of the lot USB ``has no power to grant good.''

If the lord of the lot, \Jupiter, and \Venus\, are cadent it is a harmful indication and worse if the \Moon\, does not aspect the benefics. If at the same time the malefics are angular or succedent then the person ``will fall upon misfortunes and he will be injured according to that.''

\noindent\textsc{Middling Indications:} \hfill \\
If the lord of the lot is afflicted but eastern benefics in good places aspect it, the Ascendent and the \Moon\, the person will be ``middling with respect to property and livelihood because:
\begin{itemize}[topsep=0em,itemsep=0em]
\item[\Jupiter] in a good place ``always indicates...good from nobles and mighty people and from well known work''
\item[\Venus] in a good place ``indicates benefit because of women''
\item[\Mercury] in a good place ``indicates benefit because of commerce and science and calculation'' and if mixed with \Jupiter\, the person ``will be a confident of kings and bands [of people]
\end{itemize}

\noindent\textsc{Good Indications:} \hfill \\
If the lord of the lot is in the same sign as the lot or in the 5th, the person is ``happy and wealthy'' and it is even better if the lord aspects the lot.

``The best that is [possible] is if \Saturn\, witnesses the lord of the lot of fortune in aspect, and it witnesses \Jupiter\, or the \Sun\, by day\footnote{These three are sect mates.} and by night witnesses \Mars\, or \Venus\, or the \Moon\, or \Mercury\footnote{The \Moon, \Venus, and \Mars\, are sect mates; \Mercury\, appears to be treated as one as well.}; everything one considers will be good.''

``The best that is [possible] is if the lord of the lot of fortune is in its house or triplicity or exaltation or terms.''

If the lord of the lot is in a good place while being aspected by benefics that are also in good places, the person ``will be one of the kings and the free-born, greedy for righteousness, and he will be one of the mighty nobles'' but he ``will fall from his fortune'' if the malefics witness the lot or the benefics.







